Models of lens candidates from Space Warps CFHTLS

### 2016-10-03 parts/massmodel.tex
slowly fixing figure refs

\begin{figure*}
\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
\caption{}
\end{figure*}

\begin{figure*}
\includezehn{img/kappa_map/}{_kappa_map}
\caption{}
\end{figure*}

@@

>>>>

\begin{figure*}
\includezehn{img/kappa_map/}{_kappa_map}
\caption{\label{fig:kappa}}
\end{figure*}

\begin{figure*}
\includezehn{img/arrival_spaghetti/}{_arrival_spaghetti}
\caption{\label{fig:arriv}}
\end{figure*}

\begin{figure*}
\includeten{img/nsynth/}{_nsynth}
\label{fig:synth}
\caption{}
\end{figure*}

Alongside is a synthetic image produced by modelling.  In it, the
fitted lensed images are shown in colour, while the lensing galaxy and
extraneous objects have been reduced to grayscale.
(Figure~\figref{synthimg} in \S~\ref{subsec:sourcefit} shows a
synthetic image from another model of the same system.) These two
panels are qualitative and display no units, and moreover, the mutual
alignment of the two panels is only approximate.

@@

Figures~\figref{SW58} and \figref{SW19} appear plausible lens
candidates.  Their morphology is similar to SW28, but the saddle-point
counterimage is not visible.  We consider these lenses plausible but
less convincing.

Figures~\figref{SW36} and \figref{SW57} are cases where modelling
failed.

\begin{enumerate}
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius \ER is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.
\item 
\end{enumerate}

### 2016-10-03 parts/morph.tex
slowly fixing figure refs

Figure~\ref{fig:input} shows cutouts of the Space~Warps image, marked
up with a spaghetti diagram.

@@

Figure~\ref{fig:input}

@@

\begin{figure*}
\includeten{spaghetti/}{_input}
\label{fig:input}
\caption{Marked-up images.}
\end{figure*}

>>>>

Figure~\ref{fig:markedup} shows cutouts of the Space~Warps image,
marked up with a spaghetti diagram.

@@

We show modelling results for nine of the lens candidates.  The first
five (see Figures~\figref{SW05}--\figref{SW29}) are the most
convincingly modelled systems.  The next three cases
(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
plausible models, and are representative of the majority of the
sample.  The last two are examples where the models were unconvincing
(Figures~\figref{SW36}) or completely failed (\figref{SW57}).

@@

\begin{figure*}
\includeten{spaghetti/}{_input}
\caption{Marked-up images. \label{fig:markedup}}
\end{figure*}

### 2016-10-03 parts/stelmass.tex
slowly fixing figure refs

\begin{figure*}
\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
\caption{}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
\caption{Total mass in the model against the estimated stellar mass,
  alongside the values for the whole sample.  The lower-right shaded
  region is unphysical according to the stellar-population models,
  because it gives $M<\Mstel$. The upper-left shaded region is
  unphysical according to abundance matching, because it gives
  $M>\Mhalo$.  That is to say, the unshaded region is
  $0<\haloindex<1$. \label{fig:stelmass}}
\end{figure*}

SW05, SW28, SW02, SW09 and SW29 all correspond to the mass range of
massive ellipticals.  SW05 is the most massive of all the candidates,
with a galaxy-group scale mass.

For SW42 the inferred mass is at the low end of the sample.  (The
synthetic image shown is cruder than for the five previous figures,
but that does not influence the mass models.)  If these preliminary
findings are confirmed by follow-up observations, this could be the
most dark-matter dominated lens known.\todo{Check photometry of this
  candidate.}
